Gravitaitonal Wave Event Progenitor Synthesis

### 2022-05-25 src/tex/ms.tex
Will cites Lieke and others on redshift evolution of SFR.

% Rate analysis is now just counting, like what's done in phenomenological model, instead of forward modelling.
Working event-by-event as we do permits post-processing application of
 arbitrarily complicated models of star formation and metalliticy evolution by
 re-weighting the samples we obtain \wf{Cite at least Lieke here}. Once we have
 pulled the GW event posterior back from the observable space to the
 evolutionary parameter space, we can apply the same hierarchical inference
 methods currently used to infer the compact binary population to our progenitor
 population.  In particular, we can use our progenitor population to infer the
 formation rate of compact binary population progenitor systems over cosmic time
 without needing to make artifical and simplistic assumptions about the delay
 time distribution or the metallicity-specific star formation rate \wf{again,
 cite Lieke, and also Vitale, Farr, Ng, Rodriguez?}.  Comparing the formation
 rate of progenitors to the star formation rate provides an avenue to check our
 understanding of binary evolution and the relative rate of other formation
 channels.

>>>>

% Rate analysis is now just counting, like what's done in phenomenological model, instead of forward modelling.
Working event-by-event as we do permits post-processing application of
arbitrarily complicated models of star formation and metalliticy evolution by
re-weighting the samples we obtain \citep[e.g.][]{VanSon2022}. Once we have
pulled the GW event posterior back from the observable space to the evolutionary
parameter space, we can apply the same hierarchical inference methods currently
used to infer the compact binary population to our progenitor population.  In
particular, we can use our progenitor population to infer the formation rate of
compact binary population progenitor systems over cosmic time without needing to
make artifical and simplistic assumptions about the delay time distribution or
the metallicity-specific star formation rate
\citep{Vitale2019,Ng2021,VanSon2022}.  Comparing the formation rate of
progenitors to the star formation rate provides an avenue to check our
understanding of binary evolution and the relative rate of other formation
channels.
